Title

### 2018-08-09 thesis/paper/paper.tex
Modded demand-driven

To save space and avoid redundancy the following rules will not explicitly state the inequality requirement predicate. Instead, assume that for every premise with the form \(B_1 \wedge \ldots\wedge B_m \wedge I\) where \(B_1 .. B_m\) are arbitrary atoms, \(I\) is an atom of the form \(\text{unequal}(t_1, t_2)\) with \(t_1,t_2\) terms and all of \(t_1,t_2\) that are variables appear in at least one of \(B_1 \ldots B_m\), the rule 
\begin{equation*}
\text{req\_inequality}(t_1, t_2)
 \leftarrow B_1 \wedge \ldots \wedge B_m
\end{equation*} is introduced.\\

>>>>

To save space and avoid redundancy the following rules will not explicitly state the inequality requirement predicate. Instead, assume that for every premise with the form \(B_1 \wedge \ldots\wedge B_m \wedge I_1 \wedge I_n\) where \(B_1 .. B_m\) are arbitrary atoms, \(I_1 .. I_n\) are atoms of the form \(\text{unequal}(t_{n_1}, t_{n_2})\) with \(t_{n_1}, t_{n_2}\) terms and all of \(t_{n_1}, t_{n_2}\) that are variables appear in at least one of \(B_1 \ldots B_m\), the rules 
\begin{equation*}
\text{req\_inequality}(t_{n_1}, t_{n_2})
 \leftarrow B_1 \wedge \ldots \wedge B_m
\end{equation*} for all \(n\) are introduced.\\
